Manuscript

### 2019-01-04 manuscript_analysis.Rmd

```{r}
test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
```

@@

knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ccle_data_allgenes <- readRDS("./data_munging/rds/ccle_data_18Q3_allgenes.rds")
ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ctrp_data_allgenes <- readRDS("./data_munging/rds/ctrp_data_18Q3_allgenes.rds")
ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
gdsc_data_allgenes <- readRDS("./data_munging/rds/gdsc_data_18Q3_allgenes.rds")
gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

print("Drug-Gene-Lineage")
g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
nrow(g2p_dgl_tally)
length(unique(g2p_dgl_tally$Drug))
length(unique(g2p_dgl_tally$Gene))
unique(g2p_filt$Phenotype.Description)
```

# PANCANCER

@@

```{r}
dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

```{r, results='hide', eval=FALSE}
dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
```

@@

knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

# MUT/GE/CN

## Pancancer

### Drug: Mut

### Drug: GE and CN

### Drug: P-values

### Summary stats

```{r}
# Mutation status
g2p_mut_all_summ_stats <- g2p_mut_all_summ
g2p_mut_all_summ_stats$n_true <- TRUE
g2p_mut_all_summ_stats <- g2p_mut_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)

# Pearson correlations
g2p_cor_stats <- g2p_cor
g2p_cor_stats$n_true <- TRUE
g2p_cor_stats <- g2p_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          ge_n_sig_perc = ge_n_signif / ge_n * 100,
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
          cn_n_sig_perc = cn_n_signif / cn_n * 100)
```

### CTRP example derivation

### Kolmogorov-Smirnov tests

@@

## Pancancer vs. Lineage

# OLD: BOXPLOTS

@@

# OLD: CRISPR POINT MUT MAPPING

>>>>

```{r}
test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()

# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
```

```{r}
drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)

for(drug in g2p_drugs) {
  counter = 0
  if(drug %in% as.character(unique(ccle_data_g2p$Drug))) { counter <- counter + 1 }
  if(drug %in% as.character(unique(ctrp_data_g2p$Drug))) { counter <- counter + 1 }
  if(drug %in% as.character(unique(gdsc_data_g2p$Drug))) { counter <- counter + 1 }
  drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
}
```

@@

crispr_data_signif_g2p_lineage_summ_kable <- knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ccle_data_allgenes <- readRDS("./data_munging/rds/ccle_data_18Q3_allgenes.rds")
ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
ccle_data_allgenes_kable <- knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
ccle_signif_g2p_kable <- knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
ccle_signif_g2p_grid_kable <- knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

ccle_signif_g2p_lineage_kable <- knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ccle_signif_grid_lineage_kable <- knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ctrp_data_allgenes <- readRDS("./data_munging/rds/ctrp_data_18Q3_allgenes.rds")
ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
ctrp_data_allgenes_kable <- knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
ctrp_signif_g2p_kable <- knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
ctrp_signif_g2p_grid_kable <- knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

ctrp_signif_g2p_lineage_kable <- knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ctrp_signif_grid_lineage_kable <- knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
gdsc_data_allgenes <- readRDS("./data_munging/rds/gdsc_data_18Q3_allgenes.rds")
gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
gdsc_data_allgenes_kable <- knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
gdsc_signif_g2p_kabl <- knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
gdsc_signif_g2p_grid_kable <- knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

gdsc_signif_g2p_lineage_kable <- knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

gdsc_signif_grid_lineage_kable <- knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

crispr_data_g2p_summ_kable <- knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

print("Drug-Gene-Lineage")
g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
nrow(g2p_dgl_tally)
length(unique(g2p_dgl_tally$Drug))
length(unique(g2p_dgl_tally$Gene))
# unique(g2p_filt$Phenotype.Description)
```

# MUT/GE/CN: Pancancer

## Summaries by dataset

## Summaries by feature

### Mut

### GE and CN

## P-values

## Summary stats

```{r}
# Mutation status
g2p_mut_all_summ_stats <- g2p_mut_all_summ
g2p_mut_all_summ_stats$n_true <- TRUE
g2p_mut_all_summ_stats <- g2p_mut_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
g2p_mut_all_summ_stats

# Pearson correlations
g2p_cor_stats <- g2p_cor
g2p_cor_stats$n_true <- TRUE
g2p_cor_stats <- g2p_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          ge_n_sig_perc = ge_n_signif / ge_n * 100,
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
          cn_n_sig_perc = cn_n_signif / cn_n * 100)
g2p_cor_stats
```

## CTRP example derivation

# MUT/GE/CN: By lineage

## Big grid summary plot

## Kolmogorov-Smirnov tests

# Pancancer vs. Lineage

# OLD: Distribution t-tests

@@

```{r}
dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
dgl_mut_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Make summary plots of gene expression and copy number tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
```{r, results='hide', eval=FALSE}
dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
```

@@

dgl_ge_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

dgl_cn_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

# OLD: Boxplots

@@

# OLD: CRISPR point mut mapping
